# Momentum Portfolio Building Tool


```{r, echo=FALSE, message=FALSE, warning=FALSE}

knitr::opts_chunk$set(echo    = FALSE,
                      warning = FALSE,
                      message = FALSE)
library(magrittr)

# knitr::knit(input="readme.rmd", output = "readme.md")
```


Amongst the many trading strategies that the traders use, one of the most popular strategies is the momentum strategy. Traders measure momentum in many different ways to identify opportunity pockets. The core idea across all these strategies remains the same i.e to identify momentum and ride the wave. 

I have developed and back-tested several momentum trading strategies. I am currently using 4 of these strategies, which are run with different parameters, resulting in a total of 180 parameter-specific strategies. For proprietary reasons this is is not show publicly.

The current self-curated trading universe contains more than 8,500 stocks. It contains the most important stock identifiers, including ticker symbols for the country of origin stock exchange and ticker symbols for the German stock exchanges XETRA and Frankfurt. The tickers from these table are used to download daily historical data from data providers (yahoo).

```{r}

tradr:::stock_universe %>% head(5) %>%
    kableExtra::kbl() %>%
    kableExtra::kable_styling(bootstrap_options = c("striped", "hover", "condensed"),
                              font_size = 6)
```


These stocks are filtered using information from top buy-side providers and social trading sites to define a trading basket containing ~500 stocks. This basket is used to assemble the stock portfolio.

The portfolio is assembled using the master file 01_master.daily.R in the src folder, which will basically source all other files in the folder. The result is summarized in a markdown report. 

This is an example of the portfolio from April, 2021

```{r}

readRDS("data/curr_portfolio.rds") %>%
    head(50) %>%
    kableExtra::kbl() %>%
    kableExtra::kable_styling(bootstrap_options = c("striped", "hover", "condensed"), 
                              font_size = 7, full_width = FALSE) %>%
    kableExtra::scroll_box(width = "700px", height = "300px")

```



